Long name of the paper

### 2018-10-23 anzjs2018/sections/04_implementation.tex
We want to track the figures

>>>>

The simulations we discuss here use a subset of real data from 8~October, 2018.
This allows us to run the model with different parameters over the same data.
The parameters varied were the number of particles,
GPS error $\epsilon^2$, and system noise $\sigma^2$.
The primary goal is to reduce the rate of degeneration and ``losing'' the bus 
(i.e., no particles are near the observed location),
and reducing the variance of parameter estimates; here we use vehicle speed as the example.

\subsection{Program Timings}
\label{sec:timings}

During development of our application,
our primary concert was the computational faesibility of a particle filter.
For each iteration, 
the timings of the individual components in 2a--f above are recorded.
Since the number of vehicles traveling at any given time changes throughout the day,
we used the average timings from 13:45--14:00 to compare.

Figure~\ref{fig:timings} shows the timing results for varying number of particles.

\begin{figure}[tb]
    \centering
    \includegraphics[width=0.7\textwidth]{figures/04_model_results_timing.pdf}
    \caption{The timings for various parts of the application, and overall. %
        The trend is approximately linear with the number of particles.}
    \label{fig:figure1}
\end{figure}

\subsection{Model performance}
\label{sec:model_perf}

To check the model results, 
we need to realise that we are not trying to accurately predict
future locations of the vehicle,
but instead are trying to use a sequence of GPS positions to infer travel
times along intermediate roads.
Therefore, several tools used to assess the validity of a particle filter
are unnecessary.
Instead, we will be comparing the rate of degeneration 
(i.e., the particle sample loses the actual bus and needs to be reinitialized)
and the mean distance between the state estimate and the observation.
[We also explore the uncertainty of travel time estimates,
as well as the variability between consecutive buses]\footnote{assuming we can get the results in time}.
